\thesistitle

### 2019-07-19 sections/conclusion.tex
Barebones for furture work

\section{Future work}
\label{sec:future_work}

>>>>

\section{Future work} \label{sec:future_work}
This study presents a foundation for research in a largely unexplored field of studies: analyzing maintainability through automated software metric refactoring.

\subsection{Automated Refactoring for more metrics}

\subsection{Identifying more types/definitions for clones}

\subsection{Refactoring the harder to refactor clones}

\subsection{Naming of refactored methods/classes/etc.}
